Titeln på avhandlingens språk

### 2022-12-19 appendices.tex
glossary fixes

As per the Euler-Lagrange equation from the calculus of variations~\cite{Bellman1954Dynamic,Arfken2015Calculus}, the extreme value of $\mathcal{E}$ is obtained at 
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}.\\
\intertext{Thus, for a Rayleigh distributed $\mathcal{T}$ with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\\
\Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
\Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\intertext{We have $t_0=0$. Substituting $n=1,2,\dots$, in order, in the above equation provides us our final result}
&\;t_n=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tnRayleigh}.
x\end{alignat}
% Note that throughout the paper we use a exGaussian distribution but not Rayleigh. This is because, 
Note that, due to the close similarity in their density functions, the task times can be approximated fairly equally to an \acl{exGaussian} distribution as well as a Rayleigh distribution, with the former attracting more attention from works like~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
This is the reason why the above results are applicable in this work where we have predominantly considered \gls{exGaussian} distribution.
Furthermore, we have also verified the closeness of the results as well as the validity of the approximations made in the proofs using distribution fitting and simulations.

>>>>

As per the Euler-Lagrange equation from the calculus of variations~\cite{Bellman1954Dynamic,Arfken2015Calculus}, the extreme value of $\mathcal{E}$ is obtained at 
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}.\\
\intertext{Thus, for a Rayleigh distributed $\mathcal{T}$ with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\\
\Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
\Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\intertext{We have $t_0=0$. Substituting $n=1,2,\dots$, in order, in the above equation provides us our final result}
&\;t_n=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tnRayleigh}.
x\end{alignat}
% Note that throughout the paper we use a exGaussian distribution but not Rayleigh. This is because, 
Note that, due to the close similarity in their density functions, the task times can be approximated fairly equally to an \gls{exGaussian} distribution as well as a Rayleigh distribution, with the former attracting more attention from works like~\cite{Rohrer1994analysis,Palmer2011shapes,Marmolejo2022generalised}.
This is the reason why the above results are applicable in this work where we have predominantly considered \gls{exGaussian} distribution.
Furthermore, we have also verified the closeness of the results as well as the validity of the approximations made in the proofs using distribution fitting and simulations.

### 2022-12-19 background.tex
glossary fixes

\section{Background of \acs*{WCA}}\label{sec:background}

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/task.png}
        \caption{%
            Overview of a task in a \gls{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \gls{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \gls{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

\acf{WCA} applications represent a category of novel, context-sensitive and highly-interactive \gls{AR} applications.
In this work we focus on a particular category --- ``step-based'' \gls{WCA} --- that have as their goal the guiding of a user through a sequential task.
Examples of such applications are the LEGO and IKEA assistants~\cite{Chen2015LEGO,Chen2018application}, in which users are guided step-by-step through the process of assembling a LEGO model and an IKEA lamp, respectively.

Step-based \acp{WCA} operate analogously to how \gls{GPS} navigation assistants guide users, by seamlessly and continuously monitoring the progress of the user and autonomously providing relevant instructions and feedback.
The application follows the progress of the task in ``realtime'' by repeatedly sampling the state of the physical system, most commonly through video frames.
Whenever the assistant detects that the user has correctly or incorrectly performed an instruction, it provides a new instruction to either advance the task or correct the detected mistake.
The application otherwise remains silent and out-of-the-way of the user; that is, samples which do not generate a new instruction (e.g.~because they captured an intermediate or unfinished state, or simply noise) are silently discarded.
Herein lies one of the key characteristics of these applications: the user only consciously interacts with the application whenever they finish an instruction, and thus these are the \emph{only} points in time at which they can notice changes in system responsiveness.

@@

\acp{WCA} employ sampling, most commonly of video feeds, to keep track of the state of the real world.
Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling instants at which the \gls{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e.\ which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
We define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), and the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \gls{RTT}}, respectively, of a step \( M \).
The sum of the latter two values (i.e.\ the interval \( t_{n + 1} - t_c \)) we call \emph{\gls{TTF}}, a metric which we will repeatedly refer to in this paper as it directly describes the responsiveness of a \gls{WCA}.

@@

We used \emph{delay} and execution time as the variables for system responsiveness and human behavior, respectively.
\emph{Delay} corresponded to a temporarily fixed time duration for the processing interval of each frame.
That is, if during a series of steps delay was set to \( D \) seconds, the feedback for each frame was provided to the user \( D \) seconds after frame capture.
The correlation between this variable and execution time was then studied.
To compensate for the distribution of \( t_c \)\footnote{\( t_c \), and conversely the wait time \( \mathcal{W} \) of a step, can be assumed to be uniformly distributed in the interval \( [t_{n - 1}, t_n] \) without loss of generality.}~\cite{olguinmunoz:impact2021}, in the present work we adjust the nominal delay \( D \) by a factor \num{1.5}.
We will refer to this adjusted delay as \emph{\acf{TTF}}.

@@

    \item\label{item:speedup} At lower \acp{TTF}, humans get faster at performing steps as the task progresses, 
    For sequences of \num{12} steps in an unimpaired application state, humans executed the final four steps on average \SI{36}{\percent} faster than they did the first four.
    However, this effect is dampened by reduced system responsiveness, and actually inverts at the highest levels of system impairment; humans actually become progressively slower the longer they spend in a degraded system state.

@@

We recorded variables related to well-known individual differences, encompassing both the \acf{BFI}~\cite{oliver:bfi1999}, and the \acf{ITQ}~\cite{witmer1998measuring}.
Out of the individual-difference variables, the most salient effect on performance corresponded to \emph{neuroticism}, a \gls{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

@@

Linear regression showed a significant correlation between individual neuroticism scores and the execution time late in a series of high-delay steps, \( \rho = 0.418 \), \num{2}-tailed \( p < 0.05 \)
Neuroticism was further identified as a modulating factor for the pacing effects through a \gls{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was observed across all \acp{TTF} and impairment durations in the tasks.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \gls{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \gls{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

>>>>

\section{Background of \gls{WCA}}\label{sec:background}

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/task.png}
        \caption{%
            Overview of a task in a \gls{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \gls{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \gls{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \gls{WCA}}
\end{figure}

\glspl{WCA} applications represent a category of novel, context-sensitive and highly-interactive \gls{AR} applications.
In this work we focus on a particular category --- ``step-based'' \gls{WCA} --- that have as their goal the guiding of a user through a sequential task.
Examples of such applications are the LEGO and IKEA assistants~\cite{Chen2015LEGO,Chen2018application}, in which users are guided step-by-step through the process of assembling a LEGO model and an IKEA lamp, respectively.

Step-based \glspl{WCA} operate analogously to how \gls{GPS} navigation assistants guide users, by seamlessly and continuously monitoring the progress of the user and autonomously providing relevant instructions and feedback.
The application follows the progress of the task in ``realtime'' by repeatedly sampling the state of the physical system, most commonly through video frames.
Whenever the assistant detects that the user has correctly or incorrectly performed an instruction, it provides a new instruction to either advance the task or correct the detected mistake.
The application otherwise remains silent and out-of-the-way of the user; that is, samples which do not generate a new instruction (e.g.~because they captured an intermediate or unfinished state, or simply noise) are silently discarded.
Herein lies one of the key characteristics of these applications: the user only consciously interacts with the application whenever they finish an instruction, and thus these are the \emph{only} points in time at which they can notice changes in system responsiveness.

@@

\glspl{WCA} employ sampling, most commonly of video feeds, to keep track of the state of the real world.
Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling instants at which the \gls{WCA} captures the state of the physical system, as illustrated in \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample is taken, and \( t_n \) to the instant at which the final sample (i.e.\ which captures the final state of step \( M \)) is taken. 
\( t_{n + 1} \) is then the instant at which the result for sample \( t_n \) is returned and the instruction for step \( M + 1 \) is provided.
We define \( t_c \) as the point in time at which the user finishes performing the instruction for step \( M \), and the intervals \( t_c - t_0 \), \( t_n - t_c \), and \( t_{n + 1} - t_n \) as the \emph{execution time}, \emph{wait time}, and \emph{last sample \gls{RTT}}, respectively, of a step \( M \).
The sum of the latter two values (i.e.\ the interval \( t_{n + 1} - t_c \)) we call \emph{\gls{TTF}}, a metric which we will repeatedly refer to in this paper as it directly describes the responsiveness of a \gls{WCA}.

@@

We used \emph{delay} and execution time as the variables for system responsiveness and human behavior, respectively.
\emph{Delay} corresponded to a temporarily fixed time duration for the processing interval of each frame.
That is, if during a series of steps delay was set to \( D \) seconds, the feedback for each frame was provided to the user \( D \) seconds after frame capture.
The correlation between this variable and execution time was then studied.
To compensate for the distribution of \( t_c \)\footnote{\( t_c \), and conversely the wait time \( \mathcal{W} \) of a step, can be assumed to be uniformly distributed in the interval \( [t_{n - 1}, t_n] \) without loss of generality.}~\cite{olguinmunoz:impact2021}, in the present work we adjust the nominal delay \( D \) by a factor \num{1.5}.
We will refer to this adjusted delay as \emph{\glspl{TTF}}.

@@

    \item\label{item:speedup} At lower \glspl{TTF}, humans get faster at performing steps as the task progresses,
    For sequences of \num{12} steps in an unimpaired application state, humans executed the final four steps on average \SI{36}{\percent} faster than they did the first four.
    However, this effect is dampened by reduced system responsiveness, and actually inverts at the highest levels of system impairment; humans actually become progressively slower the longer they spend in a degraded system state.

@@

We recorded variables related to well-known individual differences, encompassing both the \glspl{BFI}~\cite{oliver:bfi1999}, and the \glspl{ITQ}~\cite{witmer1998measuring}.
Out of the individual-difference variables, the most salient effect on performance corresponded to \emph{neuroticism}, a \gls{BFI} trait linked to low tolerance for stress and high emotional reactivity, and which has previously been linked to higher \emph{delay discounting} rates~\cite{hirsh2008delay}.
Delay discounting is the tendency to devalue rewards for which one must wait; high rates, indicative of waiting intolerance, have been associated with negative social and academic outcomes.

@@

Linear regression showed a significant correlation between individual neuroticism scores and the execution time late in a series of high-delay steps, \( \rho = 0.418 \), \num{2}-tailed \( p < 0.05 \)
Neuroticism was further identified as a modulating factor for the pacing effects through a \gls{PCA}.
Out of the three identified components, which cumulatively accounted for \SI{73.13}{\percent} of the variance in the results, neuroticism was included in the first two.
The effect of neuroticism was observed across all \glspl{TTF} and impairment durations in the tasks.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \gls{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \gls{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \gls{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

### 2022-12-19 conclusion.tex
glossary fixes

In terms of the optimization framework, our current model adopts the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data reasonably well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \acl{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \gls{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.

>>>>

In terms of the optimization framework, our current model adopts the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data reasonably well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \gls{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \gls{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.

### 2022-12-19 implications_footprint.tex
glossary fixes

We start by studying application lifetimes in a controlled, ideal setup by using the timing models to generate execution times for sequences of \num{100} steps subject to constant \acp{TTF}.
These runs are completely simulated and no sampling of video frames is performed; for each step, we simply feed the models a predefined \gls{TTF} and record the generated execution time.
We use the combination of \acp{TTF} and execution times to calculate theoretical step duration times and subsequent total application lifetimes.
This is done for \num{25} linearly distributed \acp{TTF} in the \SIrange[]{0}{5}{\second} range; \num{45} independent repetitions for each combination of model configuration and \gls{TTF}.

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \acp{TTF} increase.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \acp{TTF}.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{\acl{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

The results of this investigation are presented in \cref{fig:lifetimes}.
Compared to the reference model, our realistic model is, on average, roughly \SI{11}{\percent} faster when subject to low \acp{TTF}.
At higher \acp{TTF}, the behavior of the model depends on its level of normalized neuroticism.
At low neuroticism, the behavior of the realistic model results in total task durations that are basically indistinguishable from the reference model.
However, at high neuroticism, the model once again results in a considerable difference in total task duration with respect to the reference --- this time extending durations by \textasciitilde\SI{11}{\percent} on average.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \gls{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \acs*{COTS} \acs{IEEE} \num{802.11}b/g access point.
    }\label{fig:expsetup}
\end{figure}

Next we study the effects of first- versus second-order models in a more realistic setting.
The models, reference and realistic, are deployed on the Raspberry Pi clients of the testbed depicted in \cref{fig:expsetup}.
For this, the timing models and frame generator are integrated into a custom Python3 client for the Gabriel \gls{WCA} platform~\cite{Chen2018application}, which are then paired with real instances of Gabriel deployed on the cloudlet.
Clients and cloudlet communicate over an \acs{IEEE} \num{802.11}b/g wireless network.
Our choice of wireless standard is simply motivated by a desire to amplify the potential effects of network congestion.

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed.png}
        \caption{%
            Mean application lifetimes per testbed configuration.
            Note that due to the low number of samples, means have been calculated using the geometric instead of arithmetic average. 
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using bootstrapping.
        }
    \end{subfigure}
    \par\bigskip
    \begin{subtable}{\columnwidth}
        \centering
        \begin{tabular}{lrrrr}
            \toprule
            \# clients & 1 & 4 & 7 & 10 \\
            \gls{RTT} & \SI{0.42}{\second} & \SI{1.12}{\second} & \SI{1.92}{\second} & \SI{2.68}{\second} \\
            \bottomrule
        \end{tabular}
        \caption{Mean measured \aclp{RTT} for each testbed configuration.}
    \end{subtable}
    \par\bigskip
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model.
            Confidence intervals have been omitted due to the low number of samples and the use of the geometric mean.
        }
    \end{subfigure}
    \caption{Application lifetimes in the realistic scenarios.}\label{fig:testbed_lifetimes}
\end{figure}

We deploy configurations running \num{45}-step versions of the LEGO task described in~\cite{olguinmunoz:impact2021}.
The testbed configurations include setups with \numlist{1;4;7;10} clients.
Due to having limited time, each combination of testbed and timing model configuration is only repeated \num{10} times.
The results are presented in \cref{fig:testbed_lifetimes}.
Owing to the low number of samples, specifically to minimize the effects of potential outliers, we opt here for the geometric rather than arithmetic mean to represent our results.
The results are nonetheless clear, and follow the same pattern as the previously discussed results under ideal, controlled circumstances.
With just a single client and mean \gls{RTT} of around \SI{400}{\milli\second}, all parameterizations of the realistic model achieved an average task duration \SIrange{6}{12}{\percent} shorter than the reference.
At \num{10} clients, the results mimic those at higher \acp{TTF} in the ideal controlled setup, with high neuroticism parameterizations reaching \textasciitilde\SI{8}{\percent} longer application lifetimes.

>>>>

We start by studying application lifetimes in a controlled, ideal setup by using the timing models to generate execution times for sequences of \num{100} steps subject to constant \glspl{TTF}.
These runs are completely simulated and no sampling of video frames is performed; for each step, we simply feed the models a predefined \gls{TTF} and record the generated execution time.
We use the combination of \glspl{TTF} and execution times to calculate theoretical step duration times and subsequent total application lifetimes.
This is done for \num{25} linearly distributed \glspl{TTF} in the \SIrange[]{0}{5}{\second} range; \num{45} independent repetitions for each combination of model configuration and \gls{TTF}.

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \glspl{TTF} increase.
            Error bars indicate \SI{95}{\percent} \glspl{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \glspl{TTF}.
            Error bars indicate the \SI{95}{\percent} \glspl{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{\gls{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

The results of this investigation are presented in \cref{fig:lifetimes}.
Compared to the reference model, our realistic model is, on average, roughly \SI{11}{\percent} faster when subject to low \glspl{TTF}.
At higher \glspl{TTF}, the behavior of the model depends on its level of normalized neuroticism.
At low neuroticism, the behavior of the realistic model results in total task durations that are basically indistinguishable from the reference model.
However, at high neuroticism, the model once again results in a considerable difference in total task duration with respect to the reference --- this time extending durations by \textasciitilde\SI{11}{\percent} on average.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \gls{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \gls{COTS} \gls{IEEE} \num{802.11}b/g access point.
    }\label{fig:expsetup}
\end{figure}

Next we study the effects of first- versus second-order models in a more realistic setting.
The models, reference and realistic, are deployed on the Raspberry Pi clients of the testbed depicted in \cref{fig:expsetup}.
For this, the timing models and frame generator are integrated into a custom Python3 client for the Gabriel \gls{WCA} platform~\cite{Chen2018application}, which are then paired with real instances of Gabriel deployed on the cloudlet.
Clients and cloudlet communicate over an \gls{IEEE} \num{802.11}b/g wireless network.
Our choice of wireless standard is simply motivated by a desire to amplify the potential effects of network congestion.

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed.png}
        \caption{%
            Mean application lifetimes per testbed configuration.
            Note that due to the low number of samples, means have been calculated using the geometric instead of arithmetic average. 
            Error bars indicate \SI{95}{\percent} \glspl{CI}, calculated using bootstrapping.
        }
    \end{subfigure}
    \par\bigskip
    \begin{subtable}{\columnwidth}
        \centering
        \begin{tabular}{lrrrr}
            \toprule
            \# clients & 1 & 4 & 7 & 10 \\
            \gls{RTT} & \SI{0.42}{\second} & \SI{1.12}{\second} & \SI{1.92}{\second} & \SI{2.68}{\second} \\
            \bottomrule
        \end{tabular}
        \caption{Mean measured \glspl{RTT} for each testbed configuration.}
    \end{subtable}
    \par\bigskip
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model.
            Confidence intervals have been omitted due to the low number of samples and the use of the geometric mean.
        }
    \end{subfigure}
    \caption{Application lifetimes in the realistic scenarios.}\label{fig:testbed_lifetimes}
\end{figure}

We deploy configurations running \num{45}-step versions of the LEGO task described in~\cite{olguinmunoz:impact2021}.
The testbed configurations include setups with \numlist{1;4;7;10} clients.
Due to having limited time, each combination of testbed and timing model configuration is only repeated \num{10} times.
The results are presented in \cref{fig:testbed_lifetimes}.
Owing to the low number of samples, specifically to minimize the effects of potential outliers, we opt here for the geometric rather than arithmetic mean to represent our results.
The results are nonetheless clear, and follow the same pattern as the previously discussed results under ideal, controlled circumstances.
With just a single client and mean \gls{RTT} of around \SI{400}{\milli\second}, all parameterizations of the realistic model achieved an average task duration \SIrange{6}{12}{\percent} shorter than the reference.
At \num{10} clients, the results mimic those at higher \glspl{TTF} in the ideal controlled setup, with high neuroticism parameterizations reaching \textasciitilde\SI{8}{\percent} longer application lifetimes.
